### 2011-06-21 docs/preface/preface.tex
add caveat

MAESTRO is developed at the Center for Computational Sciences and
Engineering at Lawrence Berkeley National Laboratory and at Stony
Brook University.  Development was supported by the SciDAC Program of
the DOE Office of Mathematics, Information, and Computational Sciences
and the SciDAC Program of the DOE Office of High Energy Physics under
the U.S. Department of Energy under contract No.\ DE-AC02-05CH11231 to
LBNL and by a DOE/Office of Nuclear Physics grant No.\
DE-FG02-06ER41448, to Stony Brook. \\

>>>>

This documentation is a work in progress.  MAESTRO is rapidly
evolving, so portions of the text are likely to be incomplete or
out-of-date. \\

\noindent MAESTRO is developed at the Center for Computational Sciences and
Engineering at Lawrence Berkeley National Laboratory and at Stony
Brook University.  Development was supported by the SciDAC Program of
the DOE Office of Mathematics, Information, and Computational Sciences
and the SciDAC Program of the DOE Office of High Energy Physics under
the U.S. Department of Energy under contract No.\ DE-AC02-05CH11231 to
LBNL and by a DOE/Office of Nuclear Physics grant No.\
DE-FG02-06ER41448, to Stony Brook. \\
